Reproducible Validation and Replication Studies in Nanoscale Physics

### 2021-01-31 tex/results.tex
fix broken Zenodo link

\item[$\triangleright$] The file sets for reproducing the figures for the validation and replication of results from Ellis et al., 2017 are arhived in Zenodo at \href{https://doi.org/3962797/zenodo.3962791}{10.5281/zenodo.3962797} \cite{ClementiBarba2020-Zen_e}.

>>>>

\item[$\triangleright$] The file sets for reproducing the figures for the validation and replication of results from Ellis et al., 2017 are arhived in Zenodo at \href{https://doi.org/10.5281/zenodo.3962797}{10.5281/zenodo.3962797} \cite{ClementiBarba2020-Zen_e}.
